---
title: "Homework 2: Finding Your Way in R and Python"
author: "Your Name"
output: html_document
---

Instructions: Once you have finished this assignment, render the document (Ctrl/Cmd-Shift-K or the Render button). Commit the qmd file and any other files you have changed to the repository and push your changes.

In Canvas, submit a link to your github repository containing the updated files.

# MadLibs

## Running a Python Script at the command line

Run the script [madlibs.py](madlibs.py) at the command line. Do what it asks of you, and then paste the output here, making use of the generic (no language) markdown code chunk below.

## Running a Python Script in RStudio using "Source Script"

Can you run this same script in RStudio using the Source Script button? If you can, please describe any differences you note compared to using the terminal. If you cannot, tell me what happens.

Paste any relevant output here:

If you are having trouble with this question, see the [example output](02-FindingYourWay-example-solution.qmd). This will not be provided for every assignment, but is here to give you an example of what I'm looking for. You do need to

# Modes of Execution

Consider the 6 counting words examples in the [textbook module](https://srvanderplas.github.io/unl-stat850/intro-prog.html#counting-words-ex). Look at the code, and then at the information provided for each example. What is different? What is the same? Write 2-3 sentences describing how script mode, interactive mode, and command-line mode differ in R and/or Python.

# Programming with Variables

## Pythagorean Theorem in R

$$a^2 + b^2 = c^2$$

Use the chunk below to define variables $a$, $b$, and $c$, where you set $a$ and $b$ and $c$ is determined mathematically. You may need to find the square root function in R to make this work.

```{r pythagorean-theorem-r}
# Your pythagorean theorem code goes here

```

## Quadratic Formula in Python

$$x = \frac{-b \pm \sqrt{b^2 - 4ac}}{2a}$$

Use the chunk below to define variables $a$, $b$, and $c$, and then define $x1$ and $x2$, the possible values for $x$.

```{python quad-formula-py}
# Your quadratic formula code goes here

```

# Debugging practice

Look at the data frame below, which contains 3 columns: `Name`, `Salary`, and `Hire.Year`. You've read in this data from the [data file online](https://srvanderplas.github.io/stat151-homework/3-data.tsv) and ideally, you want to plot `Hire.Year` on the x-axis and `Salary` on the y-axis (code to do this is provided).

Unfortunately, the data isn't reading in properly. Identify the problem, propose a solution, and try to implement your solution using functions on the R reference card.

Some things you may want to consider: - `gsub`, a "find and replace" function. See more details by typing `?gsub` into the R console. - You can access columns in a data frame using `$`: `df$col1` will get you `col1` of the `df` object. - You can access items in a vector using `[]`: `x[1]` will get you the first item in `x`

Note: You should be able to **identify** the problem given what you know about R from this week's reading. You may not be able to implement a solution without some additional research, so if you don't get that far that's ok.

```{r}
# This line reads in a tab-separated data file with a header naming the columns
salary <- read.table("data.tsv", sep = "\t", header = T)

# This code plots labels for each individual at location (x, y)
library(ggplot2)
ggplot(salary, aes(x = Hire.Year, y = Salary, label = Name)) + 
  geom_label()

# This displays the salary object
salary
```

------------------------------------------------------------------------

The problem with the data is:

Here is how I solved the problem:

```{r cleaning-the-data-r}
# Your implementation code goes here

```
